\documentclass[a4paper,9.5pt]{article}
\usepackage{geometry}
\geometry{margin=0.6in}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{ragged2e}

% Section title style
\titleformat{\section}{\normalfont\Large\bfseries}{}{0pt}{}
\titlespacing{\section}{0pt}{6pt}{4pt}
\setlength{\parskip}{2pt}

% List spacing
\setlist[itemize]{leftmargin=12pt, noitemsep, topsep=0pt}

% Command to align dates right
\newcommand{\job}[3]{%
  \noindent\textbf{#1} \hfill \textit{#2}\\%
  \RaggedRight #3\vspace{4pt}%
}

\begin{document}
\pagestyle{empty}

\begin{center}
    {\LARGE\textbf{Yadhu Krishnan PS}}\\[6pt]
    \hrule \\[6pt]
    \begin{tabular}{c c c c c}
        \href{mailto:yadhuu.ps@gmail.com}{yadhuu.ps@gmail.com} &
        \href{tel:+916238311034}{+91 6238311034} &
        \href{https://www.linkedin.com/in/yadhu-krishnan-s}{linkedin.com/in/yadhu-krishnan-s} &
        \href{https://github.com/yadhuu06}{github.com/yadhuu06} &
        \href{https://yadhuu.live}{yadhuu.live}
    \end{tabular}
\end{center}


\section*{Professional Summary}
Lead AI Engineer with 20+ months of experience building enterprise AI platforms. Currently leading a team of 8 at Glimmora International, delivering scalable AI solutions. Contributed to a \textbf{Guinness World Record} achievement by delivering 12 AI platforms in a 24-hour hackathon. Skilled in Python, Django, React, LangChain, and cloud deployments. Transitioned from accounting to tech through self-learning, bringing strong analytical thinking and business awareness to software development.

\section*{Technical Skills}
\begin{itemize}
    \item \textbf{Languages:} Python, JavaScript, TypeScript, SQL, HTML, CSS
    \item \textbf{Frameworks/Libraries:} Django, Django REST Framework, FastAPI, React.js, LangChain
    \item \textbf{AI/ML:} LangChain, OpenAI API, Prompt Engineering, AI Platform Development
    \item \textbf{Backend \& Database:} Django ORM, PostgreSQL, Redis, MongoDB
    \item \textbf{Cloud/Deployment:} AWS (EC2), Vercel, GCP, Docker
    \item \textbf{Integrations:} Razorpay, Google OAuth, Celery (Async Processing), WebSocket
    \item \textbf{Tools:} Git, GitHub, Postman
    \item \textbf{Practices:} RESTful APIs, JWT Authentication, Team Leadership, Agile
\end{itemize}


\section*{Work Experience}

\job{Lead AI Engineer}{Apr 2025 -- Present}{%
Glimmora International, India
\begin{itemize}
    \item Leading a team of 8 (5 developers + 3 interns) in enterprise AI platform development.
    \item Managing 2 primary projects and delivered 5 projects last month.
    \item Contributed \textbf{12 AI platforms} during Guinness World Record 24-hour hackathon (54 total platforms built).
    \item Architecting and overseeing development of scalable AI solutions using Python, Django, React, and LangChain.
\end{itemize}
}

\job{AI Full-Stack Developer}{Oct 2024 -- Apr 2025}{%
Glimmora International, India
\begin{itemize}
    \item Developed AI-powered enterprise platforms using Python, Django, React, and LangChain.
    \item Built REST APIs and integrated AI workflows for various business solutions.
    \item \textbf{Promoted to Lead AI Engineer within 6 months} due to exceptional performance.
\end{itemize}
}

\job{Accountant cum Manager}{Aug 2021 -- Dec 2023}{%
Capital Petroleum and Spiceway Enterprises Pvt Ltd, Kerala
\begin{itemize}
    \item Managed financial records and budgeting with 100\% accuracy.
    \item Supervised daily operations and led a team, improving workflow efficiency.
\end{itemize}
}

\section*{Achievements}
\begin{itemize}
    \item \textbf{Guinness World Record Holder (May 2025):} Part of Glimmora International's record-breaking 24-hour AI Platform Development Hackathon. Personally contributed 12 out of 54 enterprise AI platforms built.
    \item \textbf{Rapid Career Growth:} Promoted from AI Full-Stack Developer to Lead AI Engineer in just 6 months.
    \item \textbf{Team Leadership:} Currently managing a team of 8 members including developers and interns.
\end{itemize}

\section*{Projects}

\job{Bit Code – Real-time Coding Battle Platform  \hfill \textbf{Live:} \href{https://www.bitcode.live/}{bitcode.live}}{}{%
\textit{Tech Stack: Python, Django, React.js, PostgreSQL, Celery-Beat, Redis, Docker, WebSocket}
\begin{itemize}
    \item Built scalable backend and REST APIs enabling real-time coding battles for users.
    \item Designed WebSocket + Redis Pub/Sub architecture to support low-latency communication.
    \item Implemented \textbf{ELO-based ranking system} for fair matchmaking.
    \item Developed a \textbf{custom compiler} with 3-language support (Go, JS, Python).
    \item Built multiple modes: \textbf{timed}, \textbf{ranked}, \textbf{1v1}, \textbf{squad/team battles}, and \textbf{public/private rooms}.
\end{itemize}
}

\job{BoomBlog – FastAPI Blog Application  \hfill \textbf{Live:} \href{https://blog.yadhuu.live/}{blog.yadhuu.live}}{}{%
\textit{Tech Stack: FastAPI, PostgreSQL, JWT}
\begin{itemize}
    \item Built blog platform with modular REST APIs and JWT authentication.
    \item Implemented endpoints for posts, comments, and user management.
    \item Leveraging async processing to handle concurrent requests efficiently.
\end{itemize}
}

\job{Time Twist – E-commerce Website}{}{%
\textit{Tech Stack: Django, PostgreSQL, Razorpay, HTML, CSS, Google Auth}
\begin{itemize}
    \item Built watch e-commerce platform with Razorpay payment integration.
    \item Implemented Google OAuth-based authentication for improved user onboarding.
    \item Delivered fully responsive UI ensuring mobile-first experience.
\end{itemize}
}

\section*{Education}

\job{Full-Stack Development Bootcamp}{Apr 2024 -- Oct 2024}{%
Brototype, Kerala
\begin{itemize}
    \item Intensive hands-on bootcamp focused on Python, Django, React.js, REST APIs, and deployment.
    \item Built multiple real-world projects including e-commerce platforms and real-time systems.
\end{itemize}
}

\job{Bachelor of Commerce (B.Com)}{2018 -- 2021}{%
Mahatma Gandhi University, Kerala
\begin{itemize}
    \item Specialized in accounting and financial analysis. Transitioned into software development via self-learning.
\end{itemize}
}

\end{document}
